A linearization procedure for constrained multibody systems

### 2012-08-28 PetersonGedeHubbard2012.tex
The A matrix is now a reasonable size.

\begin{figure}
  \centering
  \input{rollingdisc.pgf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}
\section{Derivation of linearization algorithm}
\label{sec:derivations}

>>>>

\begin{figure}
  \centering
  \input{rollingdisc.pgf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is very important to note that the
quantities in the matrices represent the states at the point of linearization.
This leads to $q$'s, $u$'s, $\dot{q}$'s, and $\dot{u}$'s all showing up. The
nonlinear equations need to be evaluated at a point to determine all of these
quantities. The $\dot{u}$ quantities are not actually required to be 0, so
equilibrium is not a requirement of the linearization point chosen. To reduce
the complexity of the equations, we chose $q_0$ and $q_2$ to be equal to 0.
This means that the other quantities in the linearized equations (other $q$'s,
the $\dot{q}$'s, the $u$'s, and the $\dot{u}$'s need to be solved for with
these 2 quantities already set to 0).

The independent state vector is:
\begin{align}
\begin{bmatrix}
\delta \bm{q}_i \\
\delta \bm{u}_i
\end{bmatrix} =
\begin{bmatrix}
q_0 &
q_1 &
q_2 &
q_3 &
q_4 &
u_0 &
u_1 &
u_2
\end{bmatrix}^T
\end{align}

And the complete state vector is:
\begin{align}
\begin{bmatrix}
\delta \bm{q} \\
\delta \bm{u}
\end{bmatrix} =
\left[
\begin{array}{cccccccccccc}
q_0 &
q_1 &
q_2 &
q_3 &
q_4 &
q_5 &
u_0 &
u_1 &
u_2 &
u_3 &
u_4 &
u_5
\end{array}
\right]^T
\end{align}

The two matrices which make up the linearized equation:

\begin{equation}
  \left[
    \begin{array}{cc}
      \tilde{M}_{qq} & \bm{0}_{n \times o} \\
      \tilde{M}_{uqc} & \tilde{M}_{uuc} \\
      \tilde{M}_{uqd} & \tilde{M}_{uud}
    \end{array}
    \right]=
\left[\begin{smallmatrix}0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\s_{1} & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\c_{1} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & 0 & c_{1} & s_{1} & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & 0 & - s_{1} & c_{1} & 0 & 0 & 0 & 0 & 0 & 0\\0 & 0 & 0 & 0 & 0 & 0 & 0 & r & 0 & 1 & 0 & 0\\0 & 0 & - r u_{2} & 0 & 0 & 0 & - r & 0 & 0 & 0 & 1 & 0\\0 & 0 & r u_{1} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{4} m r^{2} & 0 & 0 & 0 & - m r & 0\\0 & 0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{2} m r^{2} & 0 & m r & 0 & 0\\0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & - \frac{1}{4} m r^{2} & 0 & 0 & 0\end{smallmatrix}\right]
\end{equation}

\begin{equation*}
   \left[
     \begin{array}{cc}
       (\tilde{A}_{qq} + \tilde{A}_{qu} C_1 ) C_0 & \tilde{A}_{qu} C_2 \\
       (\tilde{A}_{uqc} + \tilde{A}_{uuc} C_1 ) C_0 & \tilde{A}_{uuc} C_2\\
       (\tilde{A}_{uqd} + \tilde{A}_{uud} C_1 ) C_0 & \tilde{A}_{uud} C_2
     \end{array}
   \right]=
\end{equation*}
\begin{equation}
\left[\begin{smallmatrix}0 & 0 & c_{1} \dot{q}_{0} & 0 & 0 & 1 & 0 & 0\\0 & - c_{1} \dot{q}_{0} & 0 & 0 & 0 & 0 & 1 & 0\\0 & s_{1} \dot{q}_{0} & - \dot{q}_{1} & 0 & 0 & 0 & 0 & 1\\- \dot{q}_{4} & 0 & c_{1} \dot{q}_{5} - s_{1} \dot{q}_{4} & 0 & 0 & 0 & - r & 0\\c_{1} \dot{q}_{3} & - c_{1} \dot{q}_{5} + s_{1} \dot{q}_{4} & r u_{2} & 0 & 0 & r & 0 & 0\\- s_{1} \dot{q}_{3} & c_{1} \dot{q}_{4} + s_{1} \dot{q}_{5} & - r u_{1} - \dot{q}_{3} & 0 & 0 & 0 & 0 & 0\\0 & 0 & r u_{1} \dot{q}_{2} & 0 & 0 & 0 & 0 & 0\\0 & 0 & - r u_{0} \dot{q}_{2} & 0 & 0 & 0 & 0 & r \dot{q}_{2}\\0 & 0 & 0 & 0 & 0 & 0 & - r \dot{q}_{2} & 0\\0 & - c_{1} g m r & m r^{2} u_{0} u_{1} & 0 & 0 & - m r u_{5} & - \frac{5}{4} m r^{2} u_{2} & \frac{1}{4} m r \left(- r u_{1} + 4 u_{3}\right)\\0 & 0 & m r \left(r u_{1} + r u_{2} - u_{0} u_{4} + u_{1} u_{3} - \dot{u}_{5}\right) & 0 & 0 & m r^{2} u_{2} & - m r u_{5} & m r u_{4}\\0 & 0 & m r \left(- g s_{1} - u_{0} u_{5} + u_{2} u_{3} + \dot{u}_{4}\right) & 0 & 0 & \frac{1}{4} m r^{2} u_{1} & \frac{1}{4} m r^{2} u_{0} & 0\end{smallmatrix}\right]
\end{equation}

\section{Derivation of linearization algorithm}
\label{sec:derivations}
